Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex

\begin{figure}
\[
\begin{array}{l@{\qquad}rcl}
\text{Values} & \mval   &=& \clos{\mvar,\mexp,\menv}\ |\ \mlit\ |\ \mkont\\
\text{States} & \mstate &=& \ev{\mexp,\menv,\msto,\mkont}\\
                       &&|& \co{\mkont,\mval,\msto}\\
                       &&|& \ap{\mval,\mval,\msto,\mkont}\\
\text{Continuations} & \mkont &=& \kmt\\
&&|& \kfn{\mval,\maddr}\\
&&|& \kar{\mexp,\menv,\maddr}\\
&&|& \kif{\mexp,\mexp,\menv,\maddr}\\
\text{Environments} &\menv&\in& \mathit{Var} \rightharpoonup \mathit{Addr}\\
\text{Stores} &\msto&\in& \mathit{Addr} \rightharpoonup \mathcal{P}(\mathit{Val})
\end{array}
\]
\caption{Abstract machine components}
\end{figure}

@@

\begin{align*}
\mathit{push}_\mlab^\mcntr(\msto,\mkont) &=
  \mlab\mcntr,\msto\sqcup[\mlab\mcntr\mapsto\{\mkont\}] \\
\mathit{bind}^\mcntr_\mlab(\menv,\msto,\mvar,\mval) &= \menv[\mvar \mapsto \maddr],
                                           \msto\sqcup[\maddr \mapsto
                                             \{ \mval\}],
                                           \mcntr' \\
\mbox{where } \mcntr' &= \lfloor\mlab\mcntr\rfloor_k \\
              \maddr &= x\mcntr' \\
%%              \lfloor \mtcntr \rfloor_k &= \mtcntr \\
              \lfloor \mcntr \rfloor_0 &= \mtcntr \\
              \lfloor \mlab\mcntr \rfloor_{k+1} &= \mlab\lfloor \mcntr\rfloor_k
\end{align*}
where $\sqcup$ on stores is a point-wise lifting of $\sqcup$: $\msto \sqcup \msto' = \lambda \maddr. \msto(\maddr) \sqcup \msto'(\maddr)$.

>>>>

\begin{figure}
\[
\begin{array}{l@{\qquad}rcl}
\text{Values} & \mval   &=& \clos{\mvar,\mexp,\menv}\ |\ \mlit\ |\ \mkont\\
\text{States} & \mstate &=& \ev{\mexp,\menv,\msto,\mkont}\\
                       &&|& \co{\mkont,\mval,\msto}\\
                       &&|& \ap{\mval,\mval,\msto,\mkont}\\
\text{Continuations} & \mkont &=& \kmt\\
&&|& \kfn{\mval,\maddr}\\
&&|& \kar{\mexp,\menv,\maddr}\\
&&|& \kif{\mexp,\mexp,\menv,\maddr}\\
\text{Environments} &\menv&\in& \mathit{Var} \rightharpoonup \mathit{Addr}\\
\text{Stores} &\msto&\in& \mathit{Addr} \rightharpoonup \mathcal{P}(\mathit{Value})
\end{array}
\]
\caption{Abstract machine components}
\label{fig:domains}
\end{figure}

@@

\begin{align*}
\mathit{push}_\mlab^\mcntr(\msto,\mkont) &=
  \mlab\mcntr,\msto\sqcup[\mlab\mcntr\mapsto\{\mkont\}] \\
\mathit{bind}^\mcntr_\mlab(\menv,\msto,\mvar,\mval) &= \menv[\mvar \mapsto \maddr],
                                           \msto\sqcup[\maddr \mapsto
                                             \{ \mval\}],
                                           \mcntr' \\
\mbox{where } \mcntr' &= \lfloor\mlab\mcntr\rfloor_k \\
              \maddr &= x\mcntr' \\
%%              \lfloor \mtcntr \rfloor_k &= \mtcntr \\
              \lfloor \mcntr \rfloor_0 &= \mtcntr \\
              \lfloor \mlab\mcntr \rfloor_{k+1} &= \mlab\lfloor \mcntr\rfloor_k
\end{align*}
where $\sqcup$ on stores is a point-wise lifting of $\sqcup$: $\msto
\sqcup \msto' = \lambda \maddr. \msto(\maddr) \sqcup \msto'(\maddr)$.
The \(\rfloor\cdot\lfloor_k\) notation denotes the truncation of a list
of symbols to the leftmost \(k\) symbols.
